SunPy - Python for Solar Physics

### 2014-07-24 3-1-VSO.tex
fix for issue #111

Listing~\ref{code:vso_query_simple} shows an example of how to query the VSO
using the \texttt{vso} module.
Queries are constructed using one or more attribute objects. Each
attribute object is a constraint on a parameter of the data set, such as the
time, instrument, or wavelength.
Listing~\ref{code:vso_query_simple} also shows how to download the data using
the constructed query. One can use the metadata associated with the data sets to 
specify how the files will be named locally, such as creating subdirectories 
based on the instrument names.

>>>>

Listing~\ref{code:vso_query_simple} shows an example of how to query and download data using
from the VSO using the \texttt{vso} module.
Queries are constructed using one or more attribute objects. Each
attribute object is a constraint on a parameter of the data set, such as the
time, instrument, or wavelength.
Listing~\ref{code:vso_query_simple} also shows how to download the data using
the constructed query. The path to which the data files will be downloaded us defined using custom tokens
which reference the file metadata (e.g. instrument, detector, filename). This provides
users the ability to organize their data into subdirectories on download.
